Homework 8

### 2019-12-05 hw8/MSimonsHW8.tex
reworking hw8 problem 5
Fixing problems 4 and 5
Typo in number 3
typo in 2a

\item
\begin{enumerate}
\item
Let $f(x) = x^3 + 2x + 1$.  We know that $f(x)$ is irreducible in
$\mathbb{Z}/3\mathbb{Z}$ because $f(0) = f(1) = f(2) = 1$.  Therefore,
$K$ is a field.

\item TODO

@@

\item To prove that $(a,b) = (d)$, first let us prove that $(a,b) \subseteq (d)$.
Let $ar_1 + br_2$ be any element of $(a,b)$.  Since $d$ is the greatest common
divisor of $a$ and $b$, $a = dx$ and $b = dy$ for some integers $x$ and $y$.
Therefore, $ar_1 + br_2 = dxr_1 + dyr_2 = d(xr_{1} + dyr_{2})$, which is an
element of $(d)$.  Thus, $(a,b) \subseteq (d)$. \\ \\
Next, let us prove $(d) \subseteq (a,b)$.  Since $d$ is the greatest common
divisor of $a$ and $b$, $d = au + bv$ for some integers $u$ and $v$.  Let
$rd$ be any element of $(d)$.
Therefore, $rd = r(au + bv) = rau + rbv = a(ru) + b(rv) \subseteq (a,b)$.
Thus $(d) \subseteq (a,b)$. \\ \\
Since $(d) \subseteq (a,b)$ and $(a,b) \subseteq (d)$, $(a,b) = (d)$.

>>>>

\item
\begin{enumerate}
\item
Let $f(x) = x^3 + 2x + 1$.  We know that $f(x)$ is irreducible over
$\mathbb{Z}/3\mathbb{Z}$ because $f(0) = f(1) = f(2) = 1$ and $\deg f(x) = 3$.
Therefore,
$K$ is a field.

@@

\item To prove that $(a,b) = (d)$, first let us prove that $(a,b) \subseteq (d)$.
Let $ar_1 + br_2$ be any element of $(a,b)$.  Since $d$ is the greatest common
divisor of $a$ and $b$, $a = dx$ and $b = dy$ for some integers $x$ and $y$.
Therefore, $ar_1 + br_2 = dxr_1 + dyr_2 = d(xr_{1} + dyr_{2})$, which is an
element of $(d)$.  Thus, $(a,b) \subseteq (d)$. \\ \\
Next, let us prove $(d) \subseteq (a,b)$.  Since $d$ is the greatest common
divisor of $a$ and $b$, $d = au + bv$ for some integers $u$ and $v$.  Let
$rd$ be any element of $(d)$.
Therefore, $rd = r(au + bv) = rau + rbv = a(ru) + b(rv) \in (a,b)$.
Thus $(d) \subseteq (a,b)$. \\ \\
Since $(d) \subseteq (a,b)$ and $(a,b) \subseteq (d)$, $(a,b) = (d)$.

\item
Let $f(x) \in I$ and $g(x) \in \mathbb{Z}[x]$ such that
\[
f(x) = a_{0} + a_{1}x + a_{2}x^{2} + ... + a_{n-1}x^{n-1} + 2a_{n}x^n
\]
and
\[
g(x) = b_{0} + b_{1}x + b_{2}x^{2} + ... + b_{m-1}x^{m-1} + 2b_{m}x^m.
\]
Then,
\[
f(x)*g(x) = a_{0}b_{0} + (a_{0}b_{1} + a_{1}b_{0})x + (a_{0}b_{2}+a_{1}b{1}+a_{2}b_{0}) + ... + 2a_{n}b_{m}x^{n+m}
\]
and
\[
g(x)*f(x) = b_{0}a_{0} + (b_{0}a_{1} + b_{1}a_{0})x + (b_{0}a_{2}+b_{1}a{1}+b_{2}a_{0}) + ... + 2b_{m}a_{n}x^{m+n}.
\]
Since the leading coefficients of $f(x)*g(x)$ and $g(x)*f(x)$ are both even,
$f(x)*g(x) \in I$ and $g(x)*f(x) \in I$.  Therefore, $I$ is an ideal of $\mathbb{Z}[x]$.

\item Let $f(x)$, $g(x) \in I$ such that $g(x) \neq 0_{F}$.
By the Division Algorithm, $g(x) = f(x)q(x) + r(x)$ such that $r(x) = 0_{F}$
or $\deg r(x) < \deg g(x)$.  By the definition of $I$,
\[
g(7) = f(7)q(7) + r(7)
\]
\[
0 = f0*q(7) + r(7)
\]
\[
0 = r(7).
\]
Therefore, $r(x) \in I$ and $f(x)$ divides $g(x)$.  Therefore, $I$ is
finitely-generated.
